An Efficient Forecasting Approach for the Real-Time Reduction of Boundary Effects in Time-Frequency Representations

### 2020-07-17 Notes/results.tex
polish code
code and typos

The experimental results show that the bias is neither depending on the noise variance $\sigma^2$ nor the forecasting length $\ell$. Indeed, independently of $\sigma$, we always have $\mu_{\xp}[N-1+\ell]\in\left[-0.03\sigma,0.03\sigma\right]$, which is negligible with respect to the magnitude of $\bz$. This result confirms the theoretical result~\eqref{eq:mean.error}. In Fig.~\ref{fig:res.noise.sine}, we display the experimental variance $\gamma_{\xp}[N-1+\ell,N-1+\ell]$ for each value of $\sigma$. The associated theoretical asymptotic forecasting variance~\eqref{eq:cov.error.2} is also displayed in solid line. As expected, this result highlights the fact that the forecasting variance increases linearly with respect to $\sigma^2$. The {\em slight} decrease of the forecasting variance with $\ell$ is characteristic of the stationarity of the forecast signal. This shows that as $\ell$ increases, the prediction becomes less dependent on the measurement noise.

@@

\subsubsection{Adaptive harmonic model}
\label{ssse:res.ahm}
We now consider a signal satisfying the AHM so that the instantaneous frequencies and amplitudes of its components vary over time. The deterministic component $\bz$ of the random vector $\bx$ (constructed following the model~\eqref{eq:model.noise}) takes the following form, for all $n\in\{1,\ldots,N\}$:
\[
\bx[n] = \cos\left(2\pi \phi_1[n] \right) + R[n]\cos\left(2\pi \phi_2[n] \right) \ ,
\] 
where the instantaneous amplitude $R$ is given by:
\[
R[n] = 1.4 + 0.2\cos\left(4\pi\frac{n}{N}\right)\ ,
\]
and the instantaneous phases are such that:
\begin{align*}
\phi_1[n] &= \frac{p_1}{M}\left( n + \frac{0.01}{2\pi}\cos\left(2\pi\frac{n}{N}\right) \right) \\[-1mm]
\phi_2[n] & = p_2\frac{n}{M} + \frac{20}{2N\fs}n^2
\end{align*}
Besides, the noise is chosen to be Gaussian: $\bw\sim\cN(\bzero,\bI)$, and we take: $N=10^4$, $M=750$, $p_1=10$, $p_2=23$.

>>>>

The experimental results show that the bias is neither depending on the noise variance $\sigma^2$ nor the forecasting length $\ell$. Indeed, independently of $\sigma$, we always have $\mu_{\xp}[N-1+\ell]\in\left[-0.03\sigma,0.03\sigma\right]$, which is negligible with respect to the magnitude of $\bz$. This result confirms the theoretical result~\eqref{eq:mean.error}. In Fig.~\ref{fig:res.noise.sine}, we display the experimental variance $\gamma_{\xp}[N-1+\ell,N-1+\ell]$ for each value of $\sigma$. The associated theoretical asymptotic forecasting variance~\eqref{eq:cov.error.2} is also displayed in solid line. As expected, this result highlights the fact that the forecasting variance increases linearly with respect to $\sigma^2$. The {\em slight} decrease of the forecasting variance with $\ell$ is characteristic of the stationarity of the forecast signal. This shows that as $\ell$ increases, the prediction becomes less correlated with the measurement noise.

@@

\subsubsection{Adaptive harmonic model}
\label{ssse:res.ahm}
We now consider a signal satisfying the AHM so that the instantaneous frequencies and amplitudes of its components vary from time to time. The deterministic component $\bz$ of the random vector $\bx$ (constructed following the model~\eqref{eq:model.noise}) takes the following form, for all $n\in\{1,\ldots,N\}$:
\[
\bx[n] = \cos\left(2\pi \phi_1[n] \right) + R[n]\cos\left(2\pi \phi_2[n] \right) \ ,
\] 
where the instantaneous amplitude $R$ is given by:
\[
R[n] = 1.4 + 0.2\cos\left(4\pi\frac{n}{N}\right)\ ,
\]
and the instantaneous phases are such that:
\begin{align*}
\phi_1[n] &= \frac{p_1}{M}\left( n + \frac{0.01}{2\pi}\cos\left(2\pi\frac{n}{N}\right) \right) \\[-1mm]
\phi_2[n] & = p_2\frac{n}{M} + \frac{20}{2N\fs}n^2
\end{align*}
Besides, the noise is chosen to be Gaussian: $\bw\sim\cN(\bzero,\bI)$, and we take: $N=10^4$, $M=750$, $p_1=10$, $p_2=23$.
